The main threats to validity identified in the review are described next:

\textbf{Primary studies selection}: Aiming at ensuring an unbiased selection process, we defined research questions in advance and devised inclusion and exclusion criteria we believe are detailed enough to provide an assessment of how the final set of primary studies was obtained. However, we cannot rule out threats from a quality assessment perspective, we simply selected studies without assigning any scores. In addition, we wanted to be as inclusive as possible, thus no limits were placed on date of publication and we avoided imposing many restrictions on primary study selection since we wanted a broad overview of the research area. \textbf{Missing important primary studies}: We conducted the review in several search engines, even though it is rather possible we missed some primary studies. We mitigated this threat by selecting search engines which have been regarded as the most relevant scientific sources~\cite{Kitchenham}. \textbf{Reviewers reliability}: The reviewers of this study are researchers in the software reuse field. So, we are not aware of any bias we may have introduced during the analyses. \textbf{Data extraction}: Another threat for this review refers to how the data were extracted from the digital libraries, since not all the information was obvious to answer the questions and some data had to be interpreted. In order to ensure the validity, multiple sources of data were analyzed, i.e. papers, technical reports, white papers. In the event of a disagreement between the two primary reviewers, a third reviewer acted as an arbitrator to ensure full agreement was reached.