\documentclass{llncs}

\usepackage{bookmark}
\usepackage{nth}
\usepackage{cite}
\usepackage{enumerate} 
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{mwe}
\usepackage{rotating}
\usepackage{colortbl}
\usepackage{array}
\usepackage{subfig}
\usepackage{fixltx2e}
\usepackage[latin9]{inputenc} 
\usepackage{listings}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[table]{xcolor}


\usepackage{fmtcount}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\begin{document}


\title{A Systematic Review on Architecture-Driven Modernization}

\author{Rafael Durelli, Bruno}

\institute{Lab, University, Address}
\maketitle

\begin{abstract}

\underline{\textbf{Background:}} Software modernization is critical for organizations which are in need of cost-effective solutions to cope with the rapid obsolescence of software and the increasing demand for new functionalities. OMG (Object Management Group) has proposed the Architecture-Driven Modernization (ADM), an approach for model-based modernizations, which contains a set of standard metamodels. Nevertheless, to the best of our knowledge, there is no a systematic review available in this field. Thus, we argue that there is a need for evidence-based body of knowledge about different aspects of the adoption of ADM.
\underline{\textbf{Objective:}} To conduct a systematic review describing how research has been doing into ADM. \underline{\textbf{Method:}} A systematic review based on searching of major electronic databases was undertaken. \underline{\textbf{Results:}} We identified 30 primary studies which were classified by their contribution, focus area and research type. Among these studies we found out a set of processes and tools to assist ADM. \underline{\textbf{Conclusion:}} ADM has become a popular approach for modernizing legacy systems by means of Model-Driven Development (MDD). There is an overall positive perception about this approach. The findings of this paper provide interesting insights into different aspects of ADM. We expect that the findings can provide valuable information to readers on what can be expected from applying ADM and its metamodels to modernize legacy systems. Furthermore, the results can provide perception of new research in the modernization area for investigating and defining new tools/process to assist the modernization of legacy system.

\end{abstract}

\section{Introduction}\label{sec:Introduction}
\linespread{0.87}
\input{tex/introduction}

\section{The Systematic Review}\label{method}

\input{tex/method_applied}
	\subsection{Planning the Systematic Review}\label{planning}
	\input{tex/planning}
	\subsection{Conducting the Systematic Review}\label{conducting}
	\input{tex/conducting}
	\subsection{Reporting the Systematic Review}\label{reporting}
	\input{tex/reporting}

\section{Discussion}\label{sec:discussion_and_threats}
	\input{tex/discussion}

\subsection{Main Findings}\label{sec:principle_findings}
	\input{tex/principles_findinds}

\subsection{Threats to Validity}\label{threats}
		\input{tex/threats_to_validity}


\section{Concluding Remarks}\label{conclusion}
		\input{tex/conclusion}

%\section*{Acknowledgments}\label{sec:Acknowledgments}

%Authors would like to thank YYYYY.

\bibliographystyle{splncs}
\bibliography{acmSac2013}
\end{document}