\documentclass{llncs}

\usepackage{bookmark}
\usepackage{nth}
\usepackage{cite}
\usepackage{enumerate} 
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{mwe}
\usepackage{rotating}
\usepackage{colortbl}
\usepackage{array}
\usepackage{subfig}
\usepackage{fixltx2e}
\usepackage[latin9]{inputenc} 
\usepackage{listings}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[table]{xcolor}


\usepackage{fmtcount}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\begin{document}


\title{A Systematic Review on Architecture-Driven Modernization}

\author{Rafael Durelli, Bruno}

\institute{Lab, University, Address}
\maketitle

\begin{abstract}

\underline{\textbf{Background:}} Architecture-Driven Modernization (ADM) has become a popular approach for modernizing legacy systems by means of Model-Driven Development (MDD). It uses standard and language independent metamodels, such as Knowledge Discovery Metamodel (KDM). The whole process involves reverse engineering a system into a KDM instance, refactoring it obtaining a modernized KDM and generating the modernized system. Although the interest in ADM has grown in the last years, to the best of our knowledge, there is neither published systematic review nor survey which presents the current state of the art and research directions in this field. Therefore, we claim that there is a need for evidence-based body of knowledge about different aspects of the adoption of ADM. \underline{\textbf{Objective:}} Presenting a systematic review that exposes the current state of the art and research directions in the ADM field. \underline{\textbf{Method:}} A systematic review on ADM was performed using Kitchenham's guidelines which consist of three main phases: (\textit{i}) planning, (\textit{ii}) conducting and (\textit{iii}) reporting. \underline{\textbf{Results and conclusion:}} Classification schemes have been defined and the 30 primary studies have been selected and classified on the basis of focus area, contribution type and research type. Four focus area have been identified. Papers that illustrated process and tools to assist the modernization of legacy system by means of ADM are in a majority. The majority of research type are evaluation research. We claim that the findings of this paper provide interesting insights into different aspects of ADM. Also, we expect that the findings can provide valuable information to readers on what can be expected from applying ADM and its metamodels to modernize legacy systems. Furthermore, the results can provide perception of new research in the modernization area for investigating and defining new tools/process to assist the modernization of legacy systems.

\end{abstract}

\section{Introduction}\label{sec:Introduction}
\linespread{0.87}
\input{tex/introduction}

\section{The Systematic Review}\label{method}

\input{tex/method_applied}
	\subsection{Planning the Systematic Review}\label{planning}
	\input{tex/planning}
	\subsection{Conducting the Systematic Review}\label{conducting}
	\input{tex/conducting}
	\subsection{Reporting the Systematic Review}\label{reporting}
	\input{tex/reporting}

\section{Discussion}\label{sec:discussion_and_threats}
	\input{tex/discussion}

\subsection{Main Findings}\label{sec:principle_findings}
	\input{tex/principles_findinds}

\subsection{Threats to Validity}\label{threats}
		\input{tex/threats_to_validity}


\section{Concluding Remarks}\label{conclusion}
		\input{tex/conclusion}

%\subsubsection{Acknowledgments}\label{sec:Acknowledgments}

%Authors would like to thank YYYYY.

\bibliographystyle{splncs}
\bibliography{acmSac2013}
\end{document}